---
title: "Assignment 2 - Data 1204"
output:
  word_document: default
---
## About the notebook
In this notebook we will test the following hypothesis:

$$H_{0}: Regular\ exercise\ does\ not\ have\ any\ impact\ on\ blood\ pressure.$$

The process followed to determine if the null hypothesis is true is described in the word document. As the sample size is less than 30, the t-distribution table is used to determine the p-value.

## Preparing the Environment and Loading Data
Install required packages.

```{r}
# install.packages(c("lattice", "readr", "readxl"))
```

Loading the required libraries.

```{r}
library(lattice)
library(readxl)
library(readr)

options(digits=3)
```

Loading blood pressure data.

```{r}
bp_data <- read_excel("BloodPressure.xls")
bp_data
```
## Testing the Null Hypothesis (p-value calculation)
> Calculating the absolute percentage change in blood pressure of the subjects before and after the 30-day experiment.

```{r}
bp_data$percent_change <- abs((bp_data$After - bp_data$Before)/bp_data$Before)
bp_data
```
Calculating the mean, standard deviation and mean standard error of the sample provided. This will be used to calculate the t-value, which will further be used to calculate the p-value.

```{r}
mean.percent_change <- mean(bp_data$percent_change)
sd.percent_change <- sd(bp_data$percent_change)
SE.percent_change <- sd.percent_change / sqrt(length(bp_data$percent_change))
mean.percent_change
sd.percent_change
SE.percent_change
```

## One-tail Test
Null hypothesis:
$$H_{0} = 0$$
Alternate hypothesis:
$$H_{a} > 0$$

Calculating the t-value.
```{r}
# State the Ho value and calculate the z-score
Ho <- 0
t <- (mean.percent_change - Ho) / SE.percent_change
t
```

Calulating the p-value.
```{r}
p_value <- pt(-t, df=length(bp_data$percent_change)-1)
p_value
p_value < 0.05 # Check if the p-value is less than 0.05 or 5%.
```
## Short Conclusion
> **As it can be seen above, the p-value is significant and the null hypothesis can be rejected.**
