---
title: "Assignment 3 - Data 1204"
output:
  word_document: default
---
## About the notebook
In this notebook we will test the following hypothesis:

$$H_{0}: mean\ of\ sales\ with\ Ad2\ is\ equal\ to\ the\ mean\ of\ sales\ with\ Ad1.$$

The process followed to determine if the null hypothesis is true is described in the word document. We will be carrying out a One Sample t-test. Hence, first the distribution of the sample data needs to checked: it should approximately normal.

## Preparing the Environment and Loading Data
Install required packages.

```{r}
# install.packages(c("lattice", "readr", "readxl"))
```

Loading the required libraries.

```{r}
library(lattice)
library(readxl)
library(readr)

options(digits=3)
```

Loading Ad2 sales data.

```{r}
sales_data <- read_excel("adanalysis.xlsx")
sales_data
```
## View the Distribution of Data
> To use the One Sample t-test, we need to ensure the assumptions made for test are valid. One of the assumptions is that the distribution of the sample data should approximately normal.


```{r}
hist(sales_data$adtype2, freq=F, main="Apple's Weekly Sales Data of Fifteen Weeks for Ad2", xlab='Weekly Sales of "Apple Pro 11"', breaks=10) 
lines(density(sales_data$adtype2), col="blue")
```

```{r}
summary(sales_data)
```


## One Sample t-test
> A simple package and method allows us to do the One Sample t-test with one line of code. The mean we are testing 

```{r}
t.test(sales_data, mu=30000, alternative = "two.sided")
```

## One Line Conclusion
> **As it can be seen above, the p-value is significant and the null hypothesis can be rejected.**
