---
title: "Week 2 - Exercises in R"
output: html_notebook
---
Install required packages
install.packages(c("lattice", "psych", "gmodels", "readr"))
```{r}
library(lattice)
library(psych)
library(gmodels)
library(readr)
```

Loading drugs data.

```{r}
drug <- read_csv("drug.csv")
```

View(drug)

```{r}
drug
```

The following will round off values to **three** significant figures.

```{r}
options(digits=3)
```

Get mean of the data.

```{r}
mean(drug$cesd)
```

Get variance of the data.

```{r}
var(drug$cesd)
```

The following function is similar to the describe function found in Pandas (Python).

```{r}
describe(drug)
```

Different plots.
1. Box plot
```{r}
boxplot(mcs~cesd, data = drug, main = "Epidemiologic Studies", xlab = "cesd")
```

2. Histogram
```{r}
x = drug$cesd

h <- hist(x, breaks=10, col="blue", xlab="CESD", main = "Epidemiologic Studies")

xfit <- seq(min(x), max(x),length=40)

yfit <- dnorm(xfit, mean=mean(x), sd=sd(x))
yfit <- yfit*diff(h$mids[1:2])*length(x)

lines(xfit, yfit, col="red", lwd=3)
```
3. Scatter Plot
```{r}
plot(drug$mcs, drug$cesd, main = "Epidemiologic Studies", xlab = "cesd", ylab = "mcs")
abline(lm(drug$mcs~drug$cesd), col="blue")
```

Finding the slope of the line, i.e. the correlation between the two varibles.

```{r}
cor(drug$mcs, drug$cesd, use="everything")
```

Creating a Crosstab table.

```{r}
mytable <- CrossTable(drug$sex, drug$homeless)
```

```{r}
mytable
```

